Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-06 text/ms.tex
Incorporate new fig 4 into main text

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{../analysis/order-posteriors-covariates.pdf}
\caption{
Posterior probability distributions from beta regression multilevel models.
(a) Main effect posterior densities for potential covariates of heavy-tailed dynamics. The response variable was Pr($\nu < 10$) (approximately the probability of heavy tails). The beta regression model was fit on a logit scale with hierarchical intercepts for taxonomic class, taxonomic order, and species. All covariates were standardized by subtracting their mean and dividing by twice their standard deviation.
(b) Taxonomic-order-level posterior densities of Pr($\nu < 10$) after accounting for time-series length. Estimates are at the geometric mean of time series length across all the data (approximately 27 time steps). Colour shading refers to taxonomic class (yellow: fishes, green: insects, purple: birds, and red: mammals). Short vertical line segments indicate median posterior estimates. Long dotted vertical line in panel b indicates the median expected Pr($\nu < 10$) from the prior distribution.
}
\label{fig:posteriors}
\end{center}
\end{figure}
